---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "images/",
  out.width = "100%"
)
```

# texter

<!-- badges: start -->
<!-- badges: end -->

The goal of texter is to help simplify text analysis for data professionals who need quick insights into their text data.

## Installation
This package is in its testing phasing and as not been submitted to CRAN.
<!-- You can install the released version of texter from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("texter") -->
<!-- ``` -->

The development version from [GitHub](https://github.com/) can be installed with:

```
# install.packages("devtools")
#devtools::install_github("simmieyungie/texter")
remotes::install_github("simmieyungie/texter@main")
#remove.packages(texter)
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(texter)
## basic example code
```

### Users
This will help you extract all the handles tagged in a tweet.

```{r cars}

head(unlist(users(doge$text)),5)
```

### Sentiment Analyzer
The emotions conveyed tweets using sentiment analysis. You have an option to specify **details = TRUE (or FALSE)**. TRUE will return a more robust distribution of sentiments and not just **Positive or Negative**.

```{r sentimentAnalyzer}
sentimentAnalyzer(doge$text, details = T)
```
Specifying details = F

```{r}
sentimentAnalyzer(doge$text, details = F)
```

### top_words
Extract the top n words occurring in a text

```{r}

top_words(word_vec = brexit$content, remove_these = c("london", "since"),
          size = 10)
```

### Counter
Retrieve the frequency of a word from a text.

```{r}
counter(word_vec = brexit$content, words = c("brexit", "london"))

```


### top_sentiments
Retrieve the top 10 positive and negative words. Specify plot = TRUE and a simple bar chart of the words will be created, otherwise you get a dataframe of results.

```{r}
top_Sentiments(word_vec = brexit$content, plot = F)
```
```{r}
top_Sentiments(word_vec = doge$text, plot = T) #You can further customize your plot
```



<!-- ### top_words_retriever -->
<!-- Retrieve the top n words occurring in a rows of data containing a certain word -->
<!-- ```{r} -->
<!-- library(tidyverse) -->
<!-- library(tidytext) -->

<!-- brexit <- read.csv("C:\\Users\\User\\Documents\\Texter\\brexitnews.csv") -->



<!-- top_words_Retriever(word_vec = brexit$content, word_ret = "bitcoin",  -->
<!--                     remove_these = c("bitcoin", "rt"), size = 10) -->


<!-- ``` -->
